Consistency scores in text data

### 2020-08-05 outputs/documents/paper.Rmd
BERT write up

BERT stands for Bidirectional Encoder Representations from Transformers (@devlin2018bert). It was released by researchers at Google AI Language in 2018. The key innovation of BERT is its application of bidirectional training of the Transformer model, which results in a deeper sense of language context and flow. What is bidirectional training? In the context of English language, a sentence is constructed from left to right. The context on the left is used to determine the next word on the right. In this sense, GPT models are unidirectional since the probability of the next word is dependent only on the past. It is also possible to reverse the direction and model the sentence from right to left, and BERT incorporates both directions of left-to-right and right-to-left to model bidirectional contexts. BERT uses the bidirectional approach to alleviate by "masked language model" (MLM). The MLM model masks certain words in the input corpus and predict the original words that are masked. The objective is to fuse the representation from the left and right context to enable the pre-training of the deep bidirectional Transformer. For example:

> **(Keli adds example)**

Because BERT employs the Transformer architecture with the self-attention mechanism, fine-tuning is also available.[To be continued...]

**(Keli adds implementation of BERT in R)**
BERT implementation in R is also possible through Keras. Zhao HG (**Replace by citation**) created a python module called Keras-bert and the module can be called by R through reticulate package, which enables interoperability between Python and R.

>>>>

BERT stands for Bidirectional Encoder Representations from Transformers (@devlin2018bert). It was released by researchers at Google AI Language in 2018. The key innovation of BERT is its application of bidirectional training of the Transformer model, which results in a deeper sense of language context and flow. What is bidirectional training? In the context of English language, a sentence is constructed from left to right. The context on the left is used to determine the next word on the right. In this sense, GPT models are unidirectional since the probability of the next word is dependent only on the past. It is also possible to reverse the direction and model the sentence from right to left, and BERT incorporates both directions of left-to-right and right-to-left to model bidirectional contexts.

BERT is pre-trained by using two unsupervised tasks. The first task is Masked Language Model and and second task is Next Sentence Prediction. The bidirectional approach of BERT is alleviated by the "Masked Language Model" (@devlin2018bert). The Masked Language Model masks certain words in the input corpus which forces the model to predict the original words by "filling in the blank". This training process blends the representation from the left and right context and therefore increases the model's context sensitivity (@nozza2020mask). In the Next Sentence Prediction process, the model receives two sentences in sequence as input. 50% of the sentences are paired in the right sequence and the ones from the other half have sentences that are paired randomly (@devlin2018bert). The goal of this process is to have BERT evaluate if the second sentence is the next sentence of the first sentence in the original text and sharpen its capacity to predict the likelihood of the next sentence.

Because BERT employs the Transformer architecture with the self-attention mechanism, fine-tuning is also available with one additional output layer and a task-specific input (@devlin2018bert). Google AI researchers have fine-tuned BERT for 11 NLP tasks including question-answering and common-sense inference.

BERT implementation in R is also possible through Keras. Zhao HG (**Replace by citation**) created a python module called "keras-bert" and the module can be called by R through "reticulate" package (@reticulateR), which enables the operation of Python modules in R. To start, the "keras-bert" module is installed in Python environment and is called in R through the 'reticulate' package.
